### 2018-08-14 pilot_manuscript.Rmd
Wrote the results stuff and made a Graph!
but what labels should we use for the x-axis??

Next, predictor models with political lean predicting percent of MFD words was analyzed for each of the MFD categories separately (i.e., "harm-positive", "harm-negative", etc.). Coefficient values indicate the mean differences between conservative and liberal sources, and to help illustrate these differences, the overall means were plotted in Figure \@ref(fig:graph-means). For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.

@@

>>>>

Next, predictor models with political lean predicting percent of MFD words was analyzed for each of the MFD categories separately (i.e., "harm-positive", "harm-negative", etc.). Coefficient values indicate the mean differences between conservative and liberal sources, and to help illustrate these differences, the overall means were plotted in Figure \@ref(fig:graph-means). For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.
For fair words, there was no signfificant difference in the words indicating fair-negative *b* = `r printnum(summary(model4.3)$tTable[2,1])`, *t*(`r summary(model4.3)$tTable[2,3]`) = `r printnum(summary(model4.3)$tTable[2,4])`, *p* = `r printp(summary(model4.3)$tTable[2,5])` or fair-positive *b* = `r printnum(summary(model4.4)$tTable[2,1])`, *t*(`r summary(model4.4)$tTable[2,3]`) = `r printnum(summary(model4.4)$tTable[2,4])`, *p* = `r printp(summary(model4.4)$tTable[2,5])`.
For ingroup words, there was no signfificant difference in the words indicating ingroup-negative *b* = `r printnum(summary(model4.5)$tTable[2,1])`, *t*(`r summary(model4.5)$tTable[2,3]`) = `r printnum(summary(model4.5)$tTable[2,4])`, *p* = `r printp(summary(model4.5)$tTable[2,5])` or ingroup-positive *b* = `r printnum(summary(model4.6)$tTable[2,1])`, *t*(`r summary(model4.6)$tTable[2,3]`) = `r printnum(summary(model4.6)$tTable[2,4])`, *p* = `r printp(summary(model4.6)$tTable[2,5])`.
For authority words, there was not a signfificant difference in the words indicating authority-negative *b* = `r printnum(summary(model4.7)$tTable[2,1])`, *t*(`r summary(model4.7)$tTable[2,3]`) = `r printnum(summary(model4.7)$tTable[2,4])`, *p* = `r printp(summary(model4.7)$tTable[2,5])` or authority-positive *b* = `r printnum(summary(model4.8)$tTable[2,1])`, *t*(`r summary(model4.8)$tTable[2,3]`) = `r printnum(summary(model4.8)$tTable[2,4])`, *p* = `r printp(summary(model4.8)$tTable[2,5])`.
For purity words, there was a signfificant difference in the words indicating purity-negative *b* = `r printnum(summary(model4.9)$tTable[2,1])`, *t*(`r summary(model4.9)$tTable[2,3]`) = `r printnum(summary(model4.9)$tTable[2,4])`, *p* = `r printp(summary(model4.9)$tTable[2,5])`. There was no significant difference for purity-positive *b* = `r printnum(summary(model4.10)$tTable[2,1])`, *t*(`r summary(model4.10)$tTable[2,3]`) = `r printnum(summary(model4.10)$tTable[2,4])`, *p* = `r printp(summary(model4.10)$tTable[2,5])`.

@@

long_mlm$moraltype = factor(long_mlm$moraltype, 
                  levels=c("hperhi", "hperlo", "fperhi", "fperlo",
                           "iperhi", "iperlo", "aperhi", "aperlo", "pperhi", "pperlo"),
                  labels = c("Harm-positive", "Harm-negative", "Fair-positive",
                             "Fair-negative", "Ingroup-positive", "Ingroup-negative",
                             "Authority-positive", "Authority-negative", 
                             "Purity-positive", "Purity-negative")) 
cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))
overallgraph = ggplot(long_mlm, aes(moraltype, percent, fill = lean))
overallgraph +
  stat_summary(fun.y = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2) +
  xlab("Moral Category") +
  ylab("Percent") + 
  cleanup +
  scale_fill_manual(name = "Political Lean", 
                    labels = c("Liberal", "Conservative"),
                    values = c("Light Gray", "Dark Gray"))
